\bibitem{x3d} D. Brutzman \& L. Daly "X3D: extensible 3D Graphics for Web Authors". Morgan Kaufmann publishers, (2007).
\bibitem{adobe-a} Adobe flash: \url{http://www.adobe.com/products/flashplayer/}.
\bibitem{adobe-b} \url{http://www.adobe.com/}
\bibitem{Apple-a} 3d ccs-transforms for the webkit. \url{http://webkit.org/specs/CSS\-VisualEffects/CSSTransforms3D.html}
\bibitem{Bishop} Canvas 3d js library. \url{http://www.c3dl.org/}
\bibitem{Excors} Canvax3d. \url{https://labs.mozilla.com/forum/comments.php?DiscussionID=363}.
\bibitem{Microsoft-a} Silverlight. \url{http://www.microsoft.com/SILVERLIGHT/}
\bibitem{Microsoft-b} Directx. \url{http://msdn.microsoft.com/directx/}
\bibitem{ECMA} Ecma-262, ecmascript language specification. \url{http://www.ecmainternational.org/publications/standards/Ecma-262.htm}
\bibitem{Google-a} O3d; an javascript based scene-graph API. \url{http://code.google.com/apis/o3d/}
\bibitem{Google-b} Google chrome experiments. \url{http://www.chromeexperiments.com/}
\bibitem{Khronos-a} Opengl. \url{http://www.opengl.org/documentation/}
\bibitem{Khronos-b} Opengl. \url{http://www.opengl.org/documentation/}
\bibitem{Khronos-c} Opengles. Khronos Group. \url{http://www.khronos.org/opengles/}
\bibitem{TimJohansson} Taking the canvas to another dimension. \url{http://my.opera.com/timjoh/blog\-/2007/11/13/takingthe-canvas-to-another-dimension}
\bibitem{VladimirVukicevic} Canvas 3D: Gl power, webstyle. \url{http://blog.vlad1.com/2007/11/26/canvas-3d-gl-powerweb-style/}
\bibitem{Web3DConsortium-a} X3D. \url{http://www.web3d.org/x3d/specifications/}
\bibitem{Web3DConsortium-b} Scene access interface(SAI), ISO/IEC CD 19775-2 ed. 2:200x. \url{http://www.web3d.org/x3d/specifications/ISO-IEC-CD-19775-2.2-X3D-SceneAccessInterface/}
\bibitem{Web3DConsortium-c} X3D Specification \url{http://www.web3d.org/x3d/specifications/}
\bibitem{W3C-a} Cascading style sheets. \url{http://www.w3.org/Style/CSS/}
\bibitem{W3C-b} HTML 5 specification, canvas section. \url{http://dev.w3.org/html5/spec/Overview.html\#the-canvaselement}
\bibitem{W3C-c} Scalable vector graphics. \url{http://www.w3.org/Graphics/SVG/}
\bibitem{W3C-d} Declarative 3D scene in HTML5. \url{http://www.w3.org/TR/html5/no.html\#declarative-3d-scenes}
